\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{color, fullpage, hyperref}
\usepackage{graphicx}

\setlength{\parindent}{0pt}
\begin{document}
\textbf{Name: Jiaming Lu $~~~~~~~~~~~~~~~~~~~~~~~~~
~~~~~~~~~~~$ Student number: 1008494620}

Solutions:

\begin{enumerate}
	\item 
		\begin{enumerate}
	\item For an arbitrary person, the probability that he/she borns on december
		25 is $\frac{1}{365}$, because the probability of birthday is considered
		to be random. Therefore, the probability of all 10 individuals born
		on December 25 is 
		$$p = (\frac{1}{365})^{10} = \frac{1}{365^{10}}$$
	\item From last question, we know that the probability that an arbitrary
		person borns on December 25 is $\frac{1}{365}$. And in this question,
		we requires 5 of the 10 people to born on December 25, so we can have
		$^{10}C_5$ possible outcomes. Moreover, for the other five people, 
		we need them to be not born on December 25, so we have $364^5$ possible
		outcomes for them. Therefore, the probability of exactly 5 individuals
		of 10 to born on December 25 is 
		$$p = ^{10}C_5\cdot 364^5\cdot(\frac{1}{365})^{10} = 
		\frac{^{10}C_5\cdot 364^5}{365^{10}}$$
	\item Because the birthday of all 10 individuals is considered to be random,
		so we can generalize the solution for question (a), which means the 
		probability of all 10 people born on the same day is 
		$\frac{1}{365^{10}}$. And also because we have 365 days in a year, so 
		there are 365 days to allow these people to have same birthday.
		Therefore, 
		$$p = 365\cdot(\frac{1}{365})^{10} = \frac{1}{365^9}$$
	\item There are 365 sets of sequence. And there are $10!$ ways we can 
		assign each birthday to each individual. Therefore, 
		$$p = 365\cdot 10! \cdot (\frac{1}{365})^{10} = \frac{10!}{365^9}$$
	\item Each person has 30 possible days to have their birthday. So there are
		$30^{10}$ possible outcomes in total. Therefore, 
		$$p = 30^{10}\cdot(\frac{1}{365})^{10} = \frac{30^{10}}{365^{10}}$$
	\item Each person who born in September has 30 possible days to have
		their birthday. And there are 5 out of 10 people to born in September,
		so there are $^{10}C_5\cdot 30^5$ possible outcomes. Meanwhile, for the 
		other 5 people who are not born in September, there are 
		$(365-30)^5 = 335^5$ possible outcomes. Therefore, 
		$$p = ^{10}C_5\cdot 30^5 \cdot 335^5\cdot\frac{1}{365^{10}}
		= \frac{^{10}C_5\cdot 30^5 \cdot 335^5}{365^{10}}$$
\end{enumerate}
\end{enumerate}
\end{document}
